---
title: "Marketing Report"
subtitle: "Office of Marketing and Brand Management"
date: "`r Sys.Date()`"
output:
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_html: default
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
bibliography: skeleton.bib
link-citations: yes
---

```{r setup, include=FALSE}
library(tufte)
library(ggplot2)
library(formatR)
library(dplyr)
library(kableExtra)
# invalidate cache when the tufte version changes
knitr::opts_chunk$set(
	echo = FALSE,
	cache.extra = packageVersion("tufte"),
	tidy = FALSE
)
options(htmltools.dir.version = FALSE)
```


```{r, include=FALSE}
#options(tinytex.verbose = TRUE)
```

```{r}
data <- read.csv("C:/Users/christine.iyer/Box/FY20_Inquiries/FY20_SpecialUpdate_3rdPartyInquiries/CombinedAndTidied.csv", header = T, stringsAsFactors = F)

State <- read.csv("C:/Users/christine.iyer/Box/FY20_Inquiries/FY20_SpecialUpdate_3rdPartyInquiries/TidiedbyState.csv", header = T, stringsAsFactors = F)

Cappex <- data %>% filter(Initial.Referral.Source == "CPPX")

Hobson <- data %>% filter(Initial.Referral.Source == "HBSN")



Start <- data %>% group_by(Anticipated.Start, Initial.Referral.Source) %>% summarise(Inquired = sum(Inquired), Applied = sum(Applied), Admitted = sum(Admitted), Confirmed = sum(Confirmed), Enrolled = sum(Enrolled))

Start_State <- State %>% group_by(Anticipated.Start, Initial.Referral.Source, Region) %>% summarise(Inquired = sum(Inquired), Applied = sum(Applied), Admitted = sum(Admitted), Confirmed = sum(Confirmed), Enrolled = sum(Enrolled))

```




# Description


In anticipation of an evaluation of third party inquiry vendors, I was asked to provide a summary of Cappex and Hobson's performance over the past three years. 

Cappex and Hobson contract details are as follows:

* Cappex - annual contract,  November - October, 16,500 USD

* Hobson - 29,643.02 USD

  + Intersect Awareness: annual contract, for the enhanced college profile and counselor community: October - September
  
  + Intersect Connection-Active match competitive: 6 mos: August - January
  
  + Intersect Connection-Active match self matching: 6 mos: August - January



# Findings



```{r}

AnnualInquiries <- data %>% group_by(Annual_Contract, Initial.Referral.Source) %>% summarise(Inquired = sum(Inquired), Applied = sum(Applied), Admitted = sum(Admitted), Confirmed = sum(Confirmed), Enrolled = sum(Enrolled))
kable(AnnualInquiries[,c(2:7)], "latex", caption = " Total Inquiries by Contract Period", booktabs = T) %>%
kable_styling(full_width = T) %>%
pack_rows(index=c("Contract 2016 - 2017 " = 2, "Contract 2017 - 2018" = 2, "Contract 2018 - 2019" = 2, "Contract 2019 - 2020" = 2))
```


```{r}
kable(Start[c(1:12),c(2:7)], "latex", caption = "Total Inquiries by Anticipated Start Year", booktabs = T) %>%
kable_styling(full_width = T) %>%
pack_rows(index=c("Anticipated Start 2017" = 2, "Anticipated Start 2018" = 2, "Anticipated Start  2019" = 2, "Anticipated Start 2020" = 2, "Anticipated Start 2021" = 2, "Anticipated Start 2022" = 2))
```



```{r}
kable(Cappex[c(1:10, 13:16, 18:20),c(2,4:8)], "latex", caption = "Cappex Inquiries by Contract Period", booktabs = T) %>%
kable_styling(full_width = T) %>%
pack_rows(index=c("Contract CPPX 2016 - 2017 " = 5, "Contract CPPX 2017 - 2018" = 5, "Contract CPPX 2018 - 2019" = 4, "Contract CPPX 2019 - 2020" = 3))
```


```{r}
kable(Hobson[c(1:7, 9:14),c(2,4:8)], "latex", caption = "Hobson Inquiries by Contract Period", booktabs = T) %>%
kable_styling(full_width = T) %>%
pack_rows(index=c("Contract HBSN 2016 - 2017 " = 4, "Contract HBSN 2017 - 2018" = 3, "Contract HBSN 2018 - 2019" = 3, "Contract HBSN 2019 - 2020" = 3))
```



```{r eval=FALSE, include=FALSE}
kable(Start_State[c(1:12),c(2:7)], "latex", caption = "Total Inquiries by Anticipated Start Year", booktabs = T) %>%
kable_styling(full_width = T) %>%
pack_rows(index=c("Anticipated Start 2017" = 2, "Anticipated Start 2018" = 2, "Anticipated Start  2019" = 2, "Anticipated Start 2020" = 2, "Anticipated Start 2021" = 2, "Anticipated Start 2022" = 2))


```

```{r}

AnnualInquiriesbyState <- State %>% group_by(
  #Contract_Period, 
  Region,
  Initial.Referral.Source 
  
  ) %>% summarise(
  Inquired = sum(Inquired), 
  # Applied = sum(Applied), 
  # Admitted = sum(Admitted), 
  # Confirmed = sum(Confirmed), 
  Enrolled = sum(Enrolled))%>%
    arrange(factor(Region, levels = c("Maine", "New Hampshire", "Massachusetts", "Connecticut" , "Vermont", "Rhode Island", "Other" )))
kable(AnnualInquiriesbyState, "latex", 
      caption = " Total Inquiries and Enrollments by State 2016-2020", booktabs = T) %>%
  kable_styling(full_width = T) %>%
  pack_rows(index=c("Maine" = 2, "New Hampshire" = 2, "Massachusetts" = 2, "Connecticut"  = 2,   "Vermont" = 2,"Rhode Island" = 2, "Other"=2
                  ))
```

### Anticipated Start 2017

```{r}
AnnualInquiriesbyState <- State %>% 
  filter(Anticipated.Start == "Fall 2017") %>% 
  group_by(
  #Contract_Period, 
  Region,
  Initial.Referral.Source 
  
  ) %>% summarise(
  Inquired = sum(Inquired), 
  # Applied = sum(Applied), 
  # Admitted = sum(Admitted), 
  # Confirmed = sum(Confirmed), 
  Enrolled = sum(Enrolled)) %>%
    arrange(factor(Region, levels = c("Maine", "New Hampshire", "Massachusetts", "Connecticut" , "Vermont", "Rhode Island", "Other" )))
kable(AnnualInquiriesbyState, "latex", 
      caption = "Fall 2017: Total Inquiries and Enrollments by State", booktabs = T) %>%
  kable_styling(full_width = T) %>%
  pack_rows(index=c("Maine" = 2, "New Hampshire" = 2, "Massachusetts" = 2, "Connecticut"  = 2,   "Vermont" = 2,"Rhode Island" = 1, "Other"=2
                  ))
```

### Anticipated Start 2018

```{r}
AnnualInquiriesbyState <- State %>% 
  filter(Anticipated.Start == "Fall 2018") %>% 
  group_by(
  #Contract_Period, 
  Region,
  Initial.Referral.Source 
  
  ) %>% summarise(
  Inquired = sum(Inquired), 
  # Applied = sum(Applied), 
  # Admitted = sum(Admitted), 
  # Confirmed = sum(Confirmed), 
  Enrolled = sum(Enrolled)) %>%
    arrange(factor(Region, levels = c("Maine", "New Hampshire", "Massachusetts", "Connecticut" , "Vermont", "Rhode Island", "Other" )))
kable(AnnualInquiriesbyState, "latex", 
      caption = "Fall 2018: Total Inquiries and Enrollments by State", booktabs = T) %>%
  kable_styling(full_width = T) %>%
  pack_rows(index=c("Maine" = 2, "New Hampshire" = 2, "Massachusetts" = 2, "Connecticut"  = 2,   "Vermont" = 2,"Rhode Island" = 2, "Other"=2
                  ))
```


### Anticipated Start 2019

```{r}
AnnualInquiriesbyState <- State %>% 
  filter(Anticipated.Start == "Fall 2019") %>% 
  group_by(
  #Contract_Period, 
  Region,
  Initial.Referral.Source 
  
  ) %>% summarise(
  Inquired = sum(Inquired), 
  # Applied = sum(Applied), 
  # Admitted = sum(Admitted), 
  # Confirmed = sum(Confirmed), 
  Enrolled = sum(Enrolled)) %>%
    arrange(factor(Region, levels = c("Maine", "New Hampshire", "Massachusetts", "Connecticut" , "Vermont", "Rhode Island", "Other" )))




kable(AnnualInquiriesbyState, "latex", 
      caption = "Fall 2019: Total Inquiries and Enrollments by State", booktabs = T) %>%
  kable_styling(full_width = T) %>%
  pack_rows(index=c("Maine" = 2, "New Hampshire" = 2, "Massachusetts" = 2, "Connecticut"  = 2,   "Vermont" = 2,"Rhode Island" = 1, "Other"=2
                  ))
```

### Anticipated Start 2020

```{r}
AnnualInquiriesbyState <- State %>% 
  filter(Anticipated.Start == "Fall 2020") %>% 
  group_by(
  #Contract_Period, 
  Region,
  Initial.Referral.Source 
  
  ) %>% summarise(
  Inquired = sum(Inquired), 
  Applied = sum(Applied),
  Admitted = sum(Admitted),
  #Confirmed = sum(Confirmed),
  Enrolled = sum(Enrolled)) %>%
    arrange(factor(Region, levels = c("Maine", "New Hampshire", "Massachusetts", "Connecticut" , "Vermont", "Rhode Island", "Other" )))

kable(AnnualInquiriesbyState, "latex", 
      caption = "Fall 2020: Total Inquiries and Enrollments by State", booktabs = T) %>%
  kable_styling(full_width = T) %>%
  pack_rows(index=c("Maine" = 2, "New Hampshire" = 2, "Massachusetts" = 2, "Connecticut"  = 2,   "Vermont" = 2,"Rhode Island" = 1, "Other"=2
                  ))
```




```{r fig-fullwidth, echo=FALSE, fig.cap="This is a full width plot.", fig.fullwidth=TRUE, fig.height=2, fig.width=10, message=FALSE, cache=TRUE}

#代码段选项`fig.fullwidth = TRUE`可以使得一幅图占用全部页宽，例如：
ggplot(diamonds, aes(carat, price)) + geom_smooth() +
  facet_grid(~ cut)
```

## Margin Figures

Images and graphics play an integral role in Tufte's work. To place figures in the margin you can use the **knitr** chunk option `fig.margin = TRUE`. For example:

```{r fig-margin, fig.margin = TRUE, fig.cap = "MPG vs horsepower, colored by transmission.", fig.width=3.5, fig.height=3.5, cache=TRUE, message=FALSE}

mtcars2 <- mtcars
mtcars2$am <- factor(
  mtcars$am, labels = c('automatic', 'manual')
)
ggplot(mtcars2, aes(hp, mpg, color = am)) +
  geom_point() + geom_smooth() +
  theme(legend.position = 'bottom')
```



## Sidenotes



If you'd like to place ancillary information in the margin without the sidenote mark (the superscript number), you can use the `margin_note()` function from **tufte** in an inline R expression. `r margin_note("This is a margin note.  Notice that there is no number preceding the note.")` This function does not process the text with Pandoc, so Markdown syntax will not work here. If you need to write anything in Markdown syntax, please use the `marginfigure` block described previously.





## Tables

You can use the `kable()` function from the **knitr** package to format tables that integrate well with the rest of the Tufte handout style. The table captions are placed in the margin like figures in the HTML output.

Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here.
Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here.
Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here.




```{r}
knitr::kable(
  mtcars[1:6, 1:6], caption = 'A subset of mtcars.'
)
```


```{marginfigure, echo = TRUE}
Notice that there is no number preceding the note. $x \in [a, b]$有
$$\frac{d}{dx}\left( \int_{a}^{x} f(u)\,du\right)=f(x).$$
```

## Plots with Margin Notes

Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here.
If you'd like to place ancillary information in the margin without the sidenote mark (the superscript number), you can use the `margin_note()` function from **tufte** in an inline R expression. 



```{r fig-main, fig.cap = "Some general comments about this plot. $500 Notice the dollar sign renders.", cache=TRUE, echo = TRUE}
ggplot(diamonds, aes(cut, price)) + geom_boxplot()
```


```{marginfigure, echo = TRUE}
Notice that there is no number preceding the note. $x \in [a, b]$有
$$\frac{d}{dx}\left( \int_{a}^{x} f(u)\,du\right)=f(x).$$
```

# ROI

Profit Profit Profit
Profit Profit Profit
Profit Profit Profit

# Conclusion

* 代码段选项
* 代码段选项
* 代码段选项

```{r bib, include=FALSE}
# create a bib file for the R packages used in this document
knitr::write_bib(c('base', 'rmarkdown'), file = 'skeleton.bib')
```
