---
title: "Third Party Inquiries: Performance Review of Cappex and Hobson 2016 - 2020"
date: "`r Sys.Date()`"


output:
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_html: default
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
bibliography: skeleton.bib
link-citations: yes
---

```{r setup, include=FALSE}
library(tufte)
library(ggplot2)
library(tidyr)
library(knitr)
library(dplyr)
library(kableExtra)
library(gridExtra)
library(grid)
# invalidate cache when the tufte version changes
knitr::opts_chunk$set(
	echo = FALSE,
	cache.extra = packageVersion("tufte"),
	tidy = FALSE
)
options(htmltools.dir.version = FALSE)
options(tinytex.verbose = TRUE)
```



```{r}
data <- read.csv("C:/Users/christine.iyer/Box/FY20_Inquiries/FY20_SpecialUpdate_3rdPartyInquiries/CombinedAndTidied.csv", header = T, stringsAsFactors = F)

State <- read.csv("C:/Users/christine.iyer/Box/FY20_Inquiries/FY20_SpecialUpdate_3rdPartyInquiries/TidiedbyState.csv", header = T, stringsAsFactors = F)

Cappex <- data %>% filter(Initial.Referral.Source == "CPPX")

Hobson <- data %>% filter(Initial.Referral.Source == "HBSN")



Start <- data %>% group_by(Anticipated.Start, Initial.Referral.Source) %>% summarise(Inquired = sum(Inquired), Applied = sum(Applied), Admitted = sum(Admitted), Confirmed = sum(Confirmed), Enrolled = sum(Enrolled))

Start_State <- State %>% group_by(Anticipated.Start, Initial.Referral.Source, Region) %>% summarise(Inquired = sum(Inquired), Applied = sum(Applied), Admitted = sum(Admitted), Confirmed = sum(Confirmed), Enrolled = sum(Enrolled))

```

```{r}
AnnualInquiries <- data %>% group_by(Annual_Contract, Initial.Referral.Source) %>% summarise(Inquired = sum(Inquired), Applied = sum(Applied), Admitted = sum(Admitted), Confirmed = sum(Confirmed), Enrolled = sum(Enrolled))

```



__Description__


`r newthought('In anticipation of ')`an evaluation of third party inquiry vendors, I was asked to provide a summary of Cappex and Hobson's performance over the past three years. 

#

Cappex and Hobson contract details are as follows:


* Cappex - annual contract,  November - October, 16,500 USD

* Hobson - 33,560 USD

  + Intersect Awareness: annual contract, for the enhanced college profile and counselor community (October - September)
  
  + Intersect Connection-Active match competitive and Active match self matching: 6 mos (August - January)
  
  + Major's Awareness: 6 mos (August - January)
  
#

#

  
#

#

#

#

  
#

#

#
  
#

#


__Findings__




#

# Total Inquiries by Anticipated Start Year

According to Aaron Deets, our CAPPEX representative, given the unpredictable class distribution of inquiries, considering the funnel by anticipated start year is a good way to evaluate whether we see a return on investment.  Although numbers are final up until the anticipated term FA19, it is important to note that confirmations and enrollments  will surely increase for  FA20, as will all stages for FA21 and and FA22. FA20 Cappex enrollments are likely to exceed those of FA19.




```{r }

kable(Start[c(1:12),c(2:7)], caption = '', booktabs = T) %>%
  kable_styling(full_width = NULL) %>%
  pack_rows(index=c("Anticipated Start 2017" = 2, "Anticipated Start 2018" = 2, "Anticipated Start  2019" = 2, "Anticipated Start 2020" = 2, "Anticipated Start 2021" = 2, "Anticipated Start 2022" = 2))
```

#

#

#

#



# Cappex Inquiries by Contract Period

The following table shows the distribution of the of the Cappex inquiries for each contract year. The numbers are weighted heavily towards upper class students. 



```{r}

kable(Cappex[c(1:10, 13:16, 18:20),c(2,4:8)],  caption = "", booktabs = T) %>%
  kable_styling(full_width = NULL) %>%
  pack_rows(index=c("Contract CPPX 2016 - 2017 " = 5, "Contract CPPX 2017 - 2018" = 5, "Contract CPPX 2018 - 2019" = 4, "Contract CPPX 2019 - 2020" = 3))
```


#

#

#

#

#

#



# Hobson Inquiries by Contract Period

The following table shows the distribution of the of the Hobson inquiries for each contract year. The numbers are weighted heavily towards upper class students, as for Cappex, however, the Junior:Senior ratio has been more variable over the past 4 years.



```{r}
kable(Hobson[c(1:7, 9:14),c(2,4:8)], caption = "", booktabs = T) %>%
  kable_styling(full_width = NULL) %>%
  pack_rows(index=c("Contract HBSN 2016 - 2017 " = 4, "Contract HBSN 2017 - 2018" = 3, "Contract HBSN 2018 - 2019" = 3, "Contract HBSN 2019 - 2020" = 3))
```


#

#

#

#

#

#

#

#

# Total Inquiries and Enrollments by State 2016-2020

The next five tables explore third party vendor performance at the state level in order to determine if one vendor out-performs the other in out-of-state enrollments.

```{r}

AnnualInquiriesbyState <- State %>% group_by(
  #Contract_Period, 
  Region,
  Initial.Referral.Source 
  
  ) %>% summarise(
  Inquired = sum(Inquired), 
  # Applied = sum(Applied), 
  # Admitted = sum(Admitted), 
  # Confirmed = sum(Confirmed), 
  Enrolled = sum(Enrolled))%>%
    arrange(factor(Region, levels = c("Maine", "New Hampshire", "Massachusetts", "Connecticut" , "Vermont", "Rhode Island", "Other" )))
```


```{r}

kable(AnnualInquiriesbyState,
      caption = "", booktabs = T) %>%
  kable_styling() %>%
  pack_rows(index=c("Maine" = 2, "New Hampshire" = 2, "Massachusetts" = 2, "Connecticut"  = 2,   "Vermont" = 2,"Rhode Island" = 2, "Other"=2
                  ))
```

#

#

#

#

#

#

#

# Fall 2017: Total Inquiries and Enrollments by State

```{r}
AnnualInquiriesbyState <- State %>% 
  filter(Anticipated.Start == "Fall 2017") %>% 
  group_by(
  #Contract_Period, 
  Region,
  Initial.Referral.Source 
  
  ) %>% summarise(
  Inquired = sum(Inquired), 
  # Applied = sum(Applied), 
  # Admitted = sum(Admitted), 
  # Confirmed = sum(Confirmed), 
  Enrolled = sum(Enrolled)) %>%
    arrange(factor(Region, levels = c("Maine", "New Hampshire", "Massachusetts", "Connecticut" , "Vermont", "Rhode Island", "Other" )))
```



```{r}

kable(AnnualInquiriesbyState,
      caption = " ", booktabs = T) %>%
  kable_styling(full_width = NULL) %>%
  pack_rows(index=c("Maine" = 2, "New Hampshire" = 2, "Massachusetts" = 2, "Connecticut"  = 2,   "Vermont" = 2,"Rhode Island" = 1, "Other"=2
                  ))
```

#

#

#

#

#

#

#

# Fall 2018: Total Inquiries and Enrollments by State

```{r}
AnnualInquiriesbyState <- State %>% 
  filter(Anticipated.Start == "Fall 2018") %>% 
  group_by(
  #Contract_Period, 
  Region,
  Initial.Referral.Source 
  
  ) %>% summarise(
  Inquired = sum(Inquired), 
  # Applied = sum(Applied), 
  # Admitted = sum(Admitted), 
  # Confirmed = sum(Confirmed), 
  Enrolled = sum(Enrolled)) %>%
    arrange(factor(Region, levels = c("Maine", "New Hampshire", "Massachusetts", "Connecticut" , "Vermont", "Rhode Island", "Other" )))

```


```{r}

kable(AnnualInquiriesbyState, 
      caption = " ", booktabs = T) %>%
  kable_styling(full_width = NULL) %>%
  pack_rows(index=c("Maine" = 2, "New Hampshire" = 2, "Massachusetts" = 2, "Connecticut"  = 2,   "Vermont" = 2,"Rhode Island" = 2, "Other"=2
                  ))
```

#

#

#

#

#

#

#

#

# Fall 2019: Total Inquiries and Enrollments by State

```{r}
AnnualInquiriesbyState <- State %>% 
  filter(Anticipated.Start == "Fall 2019") %>% 
  group_by(
  #Contract_Period, 
  Region,
  Initial.Referral.Source 
  
  ) %>% summarise(
  Inquired = sum(Inquired), 
  # Applied = sum(Applied), 
  # Admitted = sum(Admitted), 
  # Confirmed = sum(Confirmed), 
  Enrolled = sum(Enrolled)) %>%
    arrange(factor(Region, levels = c("Maine", "New Hampshire", "Massachusetts", "Connecticut" , "Vermont", "Rhode Island", "Other" )))
```


```{r}
kable(AnnualInquiriesbyState,  
      caption = " ", booktabs = T) %>%
  kable_styling(full_width = NULL) %>%
  pack_rows(index=c("Maine" = 2, "New Hampshire" = 2, "Massachusetts" = 2, "Connecticut"  = 2,   "Vermont" = 2,"Rhode Island" = 1, "Other"=2
                  ))
```

#

#

#

#

#

#

#

#

# Fall 2020: Total Inquiries and Enrollments by State

```{r}
AnnualInquiriesbyState <- State %>% 
  filter(Anticipated.Start == "Fall 2020") %>% 
  group_by(
  #Contract_Period, 
  Region,
  Initial.Referral.Source 
  
  ) %>% summarise(
  Inquired = sum(Inquired), 
  Applied = sum(Applied),
  Admitted = sum(Admitted),
  #Confirmed = sum(Confirmed),
  Enrolled = sum(Enrolled)) %>%
    arrange(factor(Region, levels = c("Maine", "New Hampshire", "Massachusetts", "Connecticut" , "Vermont", "Rhode Island", "Other" )))
```



```{r}
kable(AnnualInquiriesbyState, 
      caption = " ", booktabs = T) %>%
  kable_styling(full_width = NULL) %>%
  pack_rows(index=c("Maine" = 2, "New Hampshire" = 2, "Massachusetts" = 2, "Connecticut"  = 2,   "Vermont" = 2,"Rhode Island" = 1, "Other"=2
                  ))
```


#

#


__Conclusions__

* Since 2016, Hobsons has consistently sent ~ 1,200 inquiry names per contract period. Cappex provides more inquiry names, ~ 10% more. Overall, ~ 50% of the the names are new to the University of Southern Maine. Cappex and Hobson have accounted for 3.5% and 2.5% respectively of first-year student inquiries over the past 2 fiscal years. 

* The ratio of Maine to out-of-state (New England) inquiries is similiarly ~ 30% : ~ 70% for both vendors. Neither has boasted more out-of-state enrollments. Between 80-85% of the enrollments are from in-state.

* The data in Table 1 reveals that Cappex provides more inquiry names than Hobson, yet historically, Hobson inquiries were more likey to enroll. This may change for Fall 2020 enrollment, but it's too soon to know. 

* The data in Tables 2 and 3, illustrate the distribution of anticipated start dates for each vendor and contract year. Although the majority of inquiries are Juniors and Seniors, the class mix and distribution varies from year to year. 

* Tables 4-5 show inquiry and enrollment data by state. The intent was to explore whether one vendor performed better than the other in terms of enrolling out-of-state students. Both vendors perform equally. 

* Year over year, tuition revenue justifies the contract cost. 

* In FY20, USM changed its contract with Hobson by adding additional services. It is too know whether the increase in Hobson cost worth the investment? 


```{r bib, include=FALSE}
# create a bib file for the R packages used in this document
knitr::write_bib(c('base', 'rmarkdown'), file = 'skeleton.bib')
```








```{r eval=FALSE, include=FALSE}
# Total Inquiries (initial referral source) by Contract Period

Contract <- rep(c("CY16", "CY17", "CY18", "CY19", "CY20"), times = 2)
Vendor <- rep(c("CPPX", "HBSN"), times = c(5,5))

Inquiries <- prettyNum(c(5824, 1957,2150,1871, 728, 873, 1216, 1222, 1221,1188), big.mark = ",") 

toUs <- data.frame(Contract, Vendor, Inquiries)


Tables <- toUs %>% 
  spread(Vendor, Inquiries) 
#%>% arrange(rev(Contract))
```

```{r eval=FALSE, fig.caption="Inquiries per Vendor", fig.height=3.5, fig.margin=TRUE, fig.width=3.5, message=FALSE, cache=TRUE, include=FALSE}
grid.table(Tables, theme =  ttheme_minimal())
```
  


```{r eval=FALSE, include=FALSE}

kable(AnnualInquiries[,c(2:7)], caption = '', booktabs = T) %>% 
  kable_styling(full_width = NULL) %>%
  pack_rows(index=c("Contract 2016 - 2017 " = 2, "Contract 2017 - 2018" = 2, "Contract 2018 - 2019" = 2, "Contract 2019 - 2020" = 2))
```
