---
title: "Third Party Inquiries: Performance Review of Cappex and Hobson 2016 - 2020"
date: "`r Sys.Date()`"


output:
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_html: default
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
bibliography: skeleton.bib
link-citations: yes
---

```{r setup, include=FALSE}
library(tufte)
library(ggplot2)
library(tidyr)
library(knitr)
library(dplyr)
library(kableExtra)
library(gridExtra)
library(grid)
# invalidate cache when the tufte version changes
knitr::opts_chunk$set(
	echo = FALSE,
	cache.extra = packageVersion("tufte"),
	tidy = FALSE
)
options(htmltools.dir.version = FALSE)
options(tinytex.verbose = TRUE)
```



```{r}
data <- read.csv("C:/Users/christine.iyer/Box/FY20_Inquiries/FY20_SpecialUpdate_3rdPartyInquiries/CombinedAndTidied.csv", header = T, stringsAsFactors = F)

State <- read.csv("C:/Users/christine.iyer/Box/FY20_Inquiries/FY20_SpecialUpdate_3rdPartyInquiries/TidiedbyState.csv", header = T, stringsAsFactors = F)

Cappex <- data %>% filter(Initial.Referral.Source == "CPPX")

Hobson <- data %>% filter(Initial.Referral.Source == "HBSN")



Start <- data %>% group_by(Anticipated.Start, Initial.Referral.Source) %>% summarise(Inquired = sum(Inquired), Applied = sum(Applied), Admitted = sum(Admitted), Confirmed = sum(Confirmed), Enrolled = sum(Enrolled))

Start_State <- State %>% group_by(Anticipated.Start, Initial.Referral.Source, Region) %>% summarise(Inquired = sum(Inquired), Applied = sum(Applied), Admitted = sum(Admitted), Confirmed = sum(Confirmed), Enrolled = sum(Enrolled))

```

```{r}
AnnualInquiries <- data %>% group_by(Annual_Contract, Initial.Referral.Source) %>% summarise(Inquired = sum(Inquired), Applied = sum(Applied), Admitted = sum(Admitted), Confirmed = sum(Confirmed), Enrolled = sum(Enrolled))

```



__Description__


`r newthought('In anticipation of')`an evaluation of third party inquiry vendors, I was asked to provide a summary of Cappex and Hobson's performance over the past three years. 

#

Cappex and Hobson contract details are as follows:


* Cappex - annual contract,  November - October, 16,500 USD

* Hobson - 33,560 USD

  + Intersect Awareness: annual contract, for the enhanced college profile and counselor community (October - September)
  
  + Intersect Connection-Active match competitive and Active match self matching: 6 mos (August - January)
  
  + Major's Awareness: 6 mos (August - January)
  
  

__Findings__






# Total Inquiries (initial referral source) by Contract Period

```{r}
Contract <- rep(c("CY16", "CY17", "CY18", "CY19", "CY20"), times = 2)
Vendor <- rep(c("CPPX", "HBSN"), times = c(5,5))

Inquiries <- prettyNum(c(5824, 1957,2150,1871, 728, 873, 1216, 1222, 1221,1188), big.mark = ",") 

toUs <- data.frame(Contract, Vendor, Inquiries)


Tables <- toUs %>% 
  spread(Vendor, Inquiries) 
#%>% arrange(rev(Contract))
```

```{r, fig.margin = TRUE, fig.width=3.5, fig.height=3.5, fig.caption = "Inquiries per Vendor", cache=TRUE, message=FALSE}
grid.table(Tables, theme =  ttheme_minimal())
```
  


```{r}

kable(AnnualInquiries[,c(2:7)], caption = '', booktabs = T) %>% 
  kable_styling(full_width = NULL) %>%
  pack_rows(index=c("Contract 2016 - 2017 " = 2, "Contract 2017 - 2018" = 2, "Contract 2018 - 2019" = 2, "Contract 2019 - 2020" = 2))
```

#

# Total Inquiries by Anticipated Start Year

According to Aaron Deets, our CAPPEX representative, given the unpredictable nature of inquiries, considering the funnel by anticipated start year is a good way to evaluate whether we see a return on investment. The table below explores the data from this perspective. It is important to note that confirmed and enrollment numbers will surely increase for 2020, as will all stages for 2021 and 2022. Cappex is on track to surpass last year.




```{r }

kable(Start[c(1:12),c(2:7)], caption = '', booktabs = T) %>%
  kable_styling(full_width = NULL) %>%
  pack_rows(index=c("Anticipated Start 2017" = 2, "Anticipated Start 2018" = 2, "Anticipated Start  2019" = 2, "Anticipated Start 2020" = 2, "Anticipated Start 2021" = 2, "Anticipated Start 2022" = 2))
```

#

#

#

#



# Cappex Inquiries by Contract Period

The following table shows the distribution of the of the Cappex inquiries for each contract year. The numbers are weighted heavily towards upper class students. 



```{r}

kable(Cappex[c(1:10, 13:16, 18:20),c(2,4:8)],  caption = "", booktabs = T) %>%
  kable_styling(full_width = NULL) %>%
  pack_rows(index=c("Contract CPPX 2016 - 2017 " = 5, "Contract CPPX 2017 - 2018" = 5, "Contract CPPX 2018 - 2019" = 4, "Contract CPPX 2019 - 2020" = 3))
```


#

#

#

#

#

#



# Hobson Inquiries by Contract Period

The following table shows the distribution of the of the Hobson inquiries for each contract year. The numbers are weighted heavily towards upper class students, as for Cappex, however, the Junior:Senior ratio has been variable over the past 4 years.



```{r}
kable(Hobson[c(1:7, 9:14),c(2,4:8)], caption = "", booktabs = T) %>%
  kable_styling(full_width = NULL) %>%
  pack_rows(index=c("Contract HBSN 2016 - 2017 " = 4, "Contract HBSN 2017 - 2018" = 3, "Contract HBSN 2018 - 2019" = 3, "Contract HBSN 2019 - 2020" = 3))
```


#

#

#

#

#

#

#

#

#

#

# Total Inquiries and Enrollments by State 2016-2020

```{r}

AnnualInquiriesbyState <- State %>% group_by(
  #Contract_Period, 
  Region,
  Initial.Referral.Source 
  
  ) %>% summarise(
  Inquired = sum(Inquired), 
  # Applied = sum(Applied), 
  # Admitted = sum(Admitted), 
  # Confirmed = sum(Confirmed), 
  Enrolled = sum(Enrolled))%>%
    arrange(factor(Region, levels = c("Maine", "New Hampshire", "Massachusetts", "Connecticut" , "Vermont", "Rhode Island", "Other" )))
```


```{r}

kable(AnnualInquiriesbyState,
      caption = "", booktabs = T) %>%
  kable_styling() %>%
  pack_rows(index=c("Maine" = 2, "New Hampshire" = 2, "Massachusetts" = 2, "Connecticut"  = 2,   "Vermont" = 2,"Rhode Island" = 2, "Other"=2
                  ))
```

#

#

#

#

#

#

#

#

# Fall 2017: Total Inquiries and Enrollments by State

```{r}
AnnualInquiriesbyState <- State %>% 
  filter(Anticipated.Start == "Fall 2017") %>% 
  group_by(
  #Contract_Period, 
  Region,
  Initial.Referral.Source 
  
  ) %>% summarise(
  Inquired = sum(Inquired), 
  # Applied = sum(Applied), 
  # Admitted = sum(Admitted), 
  # Confirmed = sum(Confirmed), 
  Enrolled = sum(Enrolled)) %>%
    arrange(factor(Region, levels = c("Maine", "New Hampshire", "Massachusetts", "Connecticut" , "Vermont", "Rhode Island", "Other" )))
```



```{r}

kable(AnnualInquiriesbyState,
      caption = " ", booktabs = T) %>%
  kable_styling(full_width = NULL) %>%
  pack_rows(index=c("Maine" = 2, "New Hampshire" = 2, "Massachusetts" = 2, "Connecticut"  = 2,   "Vermont" = 2,"Rhode Island" = 1, "Other"=2
                  ))
```

#

#

#

#

#

#

#

#

# Fall 2018: Total Inquiries and Enrollments by State

```{r}
AnnualInquiriesbyState <- State %>% 
  filter(Anticipated.Start == "Fall 2018") %>% 
  group_by(
  #Contract_Period, 
  Region,
  Initial.Referral.Source 
  
  ) %>% summarise(
  Inquired = sum(Inquired), 
  # Applied = sum(Applied), 
  # Admitted = sum(Admitted), 
  # Confirmed = sum(Confirmed), 
  Enrolled = sum(Enrolled)) %>%
    arrange(factor(Region, levels = c("Maine", "New Hampshire", "Massachusetts", "Connecticut" , "Vermont", "Rhode Island", "Other" )))

```


```{r}

kable(AnnualInquiriesbyState, 
      caption = " ", booktabs = T) %>%
  kable_styling(full_width = NULL) %>%
  pack_rows(index=c("Maine" = 2, "New Hampshire" = 2, "Massachusetts" = 2, "Connecticut"  = 2,   "Vermont" = 2,"Rhode Island" = 2, "Other"=2
                  ))
```

#

#

#

#

#

#

#

#

# Fall 2019: Total Inquiries and Enrollments by State

```{r}
AnnualInquiriesbyState <- State %>% 
  filter(Anticipated.Start == "Fall 2019") %>% 
  group_by(
  #Contract_Period, 
  Region,
  Initial.Referral.Source 
  
  ) %>% summarise(
  Inquired = sum(Inquired), 
  # Applied = sum(Applied), 
  # Admitted = sum(Admitted), 
  # Confirmed = sum(Confirmed), 
  Enrolled = sum(Enrolled)) %>%
    arrange(factor(Region, levels = c("Maine", "New Hampshire", "Massachusetts", "Connecticut" , "Vermont", "Rhode Island", "Other" )))
```


```{r}
kable(AnnualInquiriesbyState,  
      caption = " ", booktabs = T) %>%
  kable_styling(full_width = NULL) %>%
  pack_rows(index=c("Maine" = 2, "New Hampshire" = 2, "Massachusetts" = 2, "Connecticut"  = 2,   "Vermont" = 2,"Rhode Island" = 1, "Other"=2
                  ))
```

#

#

#

#

#

#

#

#

# Fall 2020: Total Inquiries and Enrollments by State

```{r}
AnnualInquiriesbyState <- State %>% 
  filter(Anticipated.Start == "Fall 2020") %>% 
  group_by(
  #Contract_Period, 
  Region,
  Initial.Referral.Source 
  
  ) %>% summarise(
  Inquired = sum(Inquired), 
  Applied = sum(Applied),
  Admitted = sum(Admitted),
  #Confirmed = sum(Confirmed),
  Enrolled = sum(Enrolled)) %>%
    arrange(factor(Region, levels = c("Maine", "New Hampshire", "Massachusetts", "Connecticut" , "Vermont", "Rhode Island", "Other" )))
```



```{r}
kable(AnnualInquiriesbyState, 
      caption = " ", booktabs = T) %>%
  kable_styling(full_width = NULL) %>%
  pack_rows(index=c("Maine" = 2, "New Hampshire" = 2, "Massachusetts" = 2, "Connecticut"  = 2,   "Vermont" = 2,"Rhode Island" = 1, "Other"=2
                  ))
```


#

#


__Conclusion__

* Percent of inquiries that are the same vendor as the initial referral source 

* Is it different for each vendor?

* Is Cappex positive ROI

* Is Hobson positive ROI

* Which generates more ROI

* Was the increase in Hobson cost worth the investment? TBA because we don't know if the out of state inquiries are for the RSP programs.

* Is there an increase in quality applicants from either vendor.

* Are conversions up or down?

```{r bib, include=FALSE}
# create a bib file for the R packages used in this document
knitr::write_bib(c('base', 'rmarkdown'), file = 'skeleton.bib')
```
