---
title: "Marketing Report"
subtitle: "Office of Marketing and Brand Management"
date: "`r Sys.Date()`"
output: 
  pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
library(dplyr)
library(knitr)
library(kableExtra)
library(tinytex)
```



```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```

```{r}
data <- read.csv("CombinedAndTidied.csv", header = T, stringsAsFactors = F)

State <- read.csv("TidiedbyState.csv", header = T, stringsAsFactors = F)

Cappex <- data %>% filter(Initial.Referral.Source == "CPPX")

Hobson <- data %>% filter(Initial.Referral.Source == "HBSN")



Start <- data %>% group_by(Anticipated.Start, Initial.Referral.Source) %>% summarise(Inquired = sum(Inquired), Applied = sum(Applied), Admitted = sum(Admitted), Confirmed = sum(Confirmed), Enrolled = sum(Enrolled))

Start_State <- State %>% group_by(Anticipated.Start, Initial.Referral.Source, Region) %>% summarise(Inquired = sum(Inquired), Applied = sum(Applied), Admitted = sum(Admitted), Confirmed = sum(Confirmed), Enrolled = sum(Enrolled))

```




## Description

In anticipation of an evaluation of third party inquiry vendors, I was asked to provide a summary of Cappex and Hobson's performance over the past three years. 

Cappex and Hobson contract details are as follows:

* Cappex - annual contract,  November - October, 16,500 USD

* Hobson - 29,643.02 USD

  + Intersect Awareness: annual contract, for the enhanced college profile and counselor community: October - September
  
  + Intersect Connection-Active match competitive: 6 mos: August - January
  
  + Intersect Connection-Active match self matching: 6 mos: August - January

## Findings





```{r}

AnnualInquiries <- data %>% group_by(Annual_Contract, Initial.Referral.Source) %>% summarise(Inquired = sum(Inquired), Applied = sum(Applied), Admitted = sum(Admitted), Confirmed = sum(Confirmed), Enrolled = sum(Enrolled))
kable(AnnualInquiries[,c(2:7)], "latex", caption = " Total Inquiries by Contract Period", booktabs = T) %>%
kable_styling(full_width = T) %>%
pack_rows(index=c("Contract 2016 - 2017 " = 2, "Contract 2017 - 2018" = 2, "Contract 2018 - 2019" = 2, "Contract 2019 - 2020" = 2))
```


```{r}
kable(Start[c(1:12),c(2:7)], "latex", caption = "Total Inquiries by Anticipated Start Year", booktabs = T) %>%
kable_styling(full_width = T) %>%
pack_rows(index=c("Anticipated Start 2017" = 2, "Anticipated Start 2018" = 2, "Anticipated Start  2019" = 2, "Anticipated Start 2020" = 2, "Anticipated Start 2021" = 2, "Anticipated Start 2022" = 2))
```



```{r}
kable(Cappex[c(1:10, 13:16, 18:20),c(2,4:8)], "latex", caption = "Cappex Inquiries by Contract Period", booktabs = T) %>%
kable_styling(full_width = T) %>%
pack_rows(index=c("Contract CPPX 2016 - 2017 " = 5, "Contract CPPX 2017 - 2018" = 5, "Contract CPPX 2018 - 2019" = 4, "Contract CPPX 2019 - 2020" = 3))
```


```{r}
kable(Hobson[c(1:7, 9:14),c(2,4:8)], "latex", caption = "Hobson Inquiries by Contract Period", booktabs = T) %>%
kable_styling(full_width = T) %>%
pack_rows(index=c("Contract HBSN 2016 - 2017 " = 4, "Contract HBSN 2017 - 2018" = 3, "Contract HBSN 2018 - 2019" = 3, "Contract HBSN 2019 - 2020" = 3))
```



```{r eval=FALSE, include=FALSE}
kable(Start_State[c(1:12),c(2:7)], "latex", caption = "Total Inquiries by Anticipated Start Year", booktabs = T) %>%
kable_styling(full_width = T) %>%
pack_rows(index=c("Anticipated Start 2017" = 2, "Anticipated Start 2018" = 2, "Anticipated Start  2019" = 2, "Anticipated Start 2020" = 2, "Anticipated Start 2021" = 2, "Anticipated Start 2022" = 2))


```

```{r}

AnnualInquiriesbyState <- State %>% group_by(
  #Contract_Period, 
  Region,
  Initial.Referral.Source 
  
  ) %>% summarise(
  Inquired = sum(Inquired), 
  # Applied = sum(Applied), 
  # Admitted = sum(Admitted), 
  # Confirmed = sum(Confirmed), 
  Enrolled = sum(Enrolled))%>%
    arrange(factor(Region, levels = c("Maine", "New Hampshire", "Massachusetts", "Connecticut" , "Vermont", "Rhode Island", "Other" )))
kable(AnnualInquiriesbyState, "latex", 
      caption = " Total Inquiries and Enrollments by State 2016-2020", booktabs = T) %>%
  kable_styling(full_width = T) %>%
  pack_rows(index=c("Maine" = 2, "New Hampshire" = 2, "Massachusetts" = 2, "Connecticut"  = 2,   "Vermont" = 2,"Rhode Island" = 2, "Other"=2
                  ))
```

### Anticipated Start 2017

```{r}
AnnualInquiriesbyState <- State %>% 
  filter(Anticipated.Start == "Fall 2017") %>% 
  group_by(
  #Contract_Period, 
  Region,
  Initial.Referral.Source 
  
  ) %>% summarise(
  Inquired = sum(Inquired), 
  # Applied = sum(Applied), 
  # Admitted = sum(Admitted), 
  # Confirmed = sum(Confirmed), 
  Enrolled = sum(Enrolled)) %>%
    arrange(factor(Region, levels = c("Maine", "New Hampshire", "Massachusetts", "Connecticut" , "Vermont", "Rhode Island", "Other" )))
kable(AnnualInquiriesbyState, "latex", 
      caption = "Fall 2017: Total Inquiries and Enrollments by State", booktabs = T) %>%
  kable_styling(full_width = T) %>%
  pack_rows(index=c("Maine" = 2, "New Hampshire" = 2, "Massachusetts" = 2, "Connecticut"  = 2,   "Vermont" = 2,"Rhode Island" = 1, "Other"=2
                  ))
```

### Anticipated Start 2018

```{r}
AnnualInquiriesbyState <- State %>% 
  filter(Anticipated.Start == "Fall 2018") %>% 
  group_by(
  #Contract_Period, 
  Region,
  Initial.Referral.Source 
  
  ) %>% summarise(
  Inquired = sum(Inquired), 
  # Applied = sum(Applied), 
  # Admitted = sum(Admitted), 
  # Confirmed = sum(Confirmed), 
  Enrolled = sum(Enrolled)) %>%
    arrange(factor(Region, levels = c("Maine", "New Hampshire", "Massachusetts", "Connecticut" , "Vermont", "Rhode Island", "Other" )))
kable(AnnualInquiriesbyState, "latex", 
      caption = "Fall 2018: Total Inquiries and Enrollments by State", booktabs = T) %>%
  kable_styling(full_width = T) %>%
  pack_rows(index=c("Maine" = 2, "New Hampshire" = 2, "Massachusetts" = 2, "Connecticut"  = 2,   "Vermont" = 2,"Rhode Island" = 2, "Other"=2
                  ))
```


### Anticipated Start 2019

```{r}
AnnualInquiriesbyState <- State %>% 
  filter(Anticipated.Start == "Fall 2019") %>% 
  group_by(
  #Contract_Period, 
  Region,
  Initial.Referral.Source 
  
  ) %>% summarise(
  Inquired = sum(Inquired), 
  # Applied = sum(Applied), 
  # Admitted = sum(Admitted), 
  # Confirmed = sum(Confirmed), 
  Enrolled = sum(Enrolled)) %>%
    arrange(factor(Region, levels = c("Maine", "New Hampshire", "Massachusetts", "Connecticut" , "Vermont", "Rhode Island", "Other" )))




kable(AnnualInquiriesbyState, "latex", 
      caption = "Fall 2019: Total Inquiries and Enrollments by State", booktabs = T) %>%
  kable_styling(full_width = T) %>%
  pack_rows(index=c("Maine" = 2, "New Hampshire" = 2, "Massachusetts" = 2, "Connecticut"  = 2,   "Vermont" = 2,"Rhode Island" = 1, "Other"=2
                  ))
```

### Anticipated Start 2020

```{r}
AnnualInquiriesbyState <- State %>% 
  filter(Anticipated.Start == "Fall 2020") %>% 
  group_by(
  #Contract_Period, 
  Region,
  Initial.Referral.Source 
  
  ) %>% summarise(
  Inquired = sum(Inquired), 
  Applied = sum(Applied),
  Admitted = sum(Admitted),
  #Confirmed = sum(Confirmed),
  Enrolled = sum(Enrolled)) %>%
    arrange(factor(Region, levels = c("Maine", "New Hampshire", "Massachusetts", "Connecticut" , "Vermont", "Rhode Island", "Other" )))

kable(AnnualInquiriesbyState, "latex", 
      caption = "Fall 2020: Total Inquiries and Enrollments by State", booktabs = T) %>%
  kable_styling(full_width = T) %>%
  pack_rows(index=c("Maine" = 2, "New Hampshire" = 2, "Massachusetts" = 2, "Connecticut"  = 2,   "Vermont" = 2,"Rhode Island" = 1, "Other"=2
                  ))
```

## Conclusions

